%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Senior Product Engineer} % Job title
{Codingmart technologies} % Organization
{Bangalore, India} % Location
{Sept 2023 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Understanding the needs of stakeholders and conveying them to developers.}
    \item {Working on ways to automate and improve development and release processes.}
    \item {Testing and examining code written by others and analyzing results.}
    \item {Ensuring that systems are safe and secure against cybersecurity threats.}
    \item {Identifying technical problems and developing software updates and fixes.}
    \item {Monitoring the processes during the entire lifecycle for its adherence and updating or creating new processes for improvement and minimizing the wastage.}
    \item {Conforming to best practices in network administration and cybersecurity.}
  \end{cvitems}
}
%---------------------------------------------------------


%---------------------------------------------------------
  \cventry
    {Devops Engineer} % Job title
    {Wipro Limited} % Organization
    {Chennai, India} % Location
    {April. 2020 - Nov. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Having experience in AWS Devops Build and Release Management process.}
        \item {Worked on different AWS services like EC2, AMI, Snapshot, EBS, ELB, EFS, Autoscaling, S3, VPC, Route53, Lambda, IAM, EKS, Cloudtrail, CloudWatch, CloudFormation, SQS, SNS }
        \item {Worked on optimizing volumes and EC2 instances and created multiple VPC's.}
        \item {Managed Github repositories and permissions, including branching and tagging.}
        \item {Used Ansible for Configuration management.}
        \item {Excellent skills in applying Continuous integration, Continuous deployment, Continuous delivery processes and tools Git, Maven,  Jenkins, Ansible, Tomcat, Docker, Kubernetes.}
        \item {Good exposure to version control tool like Git.}
        \item {Worked on Jenkins by installing, configuring and maintaining for the purpose of Continuous integration and End to End automation for all build and deployments.}
        \item {Installing and configuring Jenkins master and slave nodes.}
        \item {Involved in creating Docker images by writing custom docker file.}
        \item {Having good knowledge in Terraform.}
        \item {Strong ability to troubleshoot any issues generated while building, deploying in production Support.}
        \item {Created alarms and notifications for EC2 instances using CloudWatch.}
        \item {Interested to learn new tools and technologies.}
      \end{cvitems}
    }

%---------------------------------------------------------


%---------------------------------------------------------
  \cventry
    {Application Support Engineer} % Job title
    {Sutherland Global Service Pvt Lmt} % Organization
    {Chennai , India} % Location
    {Aug. 2017 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Providing software application Support under the supervision of the Senior Engineer.}
        \item {Performing analysis on software application functionality and suggesting improvements.}
        \item {Managing ticketed query system and ensuring comprehensive database of queries and resolutions is kept up to date.}
        \item {Consulting with the software development team, internal users, and clients to improve application performance.}
        \item {Preparing maintenance plans and upgrading schedules for the organisation's systems.}
        \item {Developing reports for the teams across the business.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
